Flowchart of Current Algorithm

### 2009-02-26 docs/flowchart/flowchart.tex
split the "changes" section into two parts:  Changes between paper 3 and paper 4, and Changes since paper 4
put advect base pres back in

\section{Algorithm Updates}

@@

@@

\begin{itemize}
\item Should we eliminate {\bf Advect Base Pressure} entirely, and instead directly
enforce HSE after {\bf Correct Base}?  {\bf Advect Base Pressure} was just a fancy
way of enforcing HSE anyway, so why not just compute the new pressure directly?

>>>>

%-----------------------------------------------------------------------------
% Changes Between Paper 3 and Paper 4
%-----------------------------------------------------------------------------

\section{Changes Between Paper 3 and Paper 4}

@@

%-----------------------------------------------------------------------------
% Changes Since Paper 4
%-----------------------------------------------------------------------------

\section{Changes Since Paper 4}

@@

\item Should we eliminate {\bf Advect Base Pressure} entirely, and instead directly
enforce HSE after {\bf Correct Base}?  {\bf Advect Base Pressure} was just a fancy
way of enforcing HSE anyway, so we just compute the new pressure directly.  The
problems we have seen with enforcing HSE directly have to do with the roundoff
error that accumulates, causing the temperature computed from the EOS to drift.
